---
title: "Evaluating RSV older adult vaccination programmes for JCVI in 2023"
author: "David Hodgson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Evaluating RSV older adult vaccination programmes for JCVI in 2023}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Markdown explaining how to use the RSV impact evaluation `rsvie` package


## 1. Load package and functions

This vignette explains how to use the `rsvie` package to evaluate the impact of different RSV intervention programmes. The package is designed to be flexible and allow the user to define different intervention programmes, with different immunological profiles, and evaluate their impact on RSV outcomes.

```{r}

devtools::load_all()
# or library(rsvie)
library(devtools)
library(tidyverse)
library(here)

```

### Run scenarios for JCVI 2023 

```{r}

RSVempty <- make_rsv_programme(S = 1) # for some reason the simulations are way slower than before, will try and fix this soon. (S in the number of samples, usually 100-1000, but will just use 1 for now.)

econ_raw_ls_15 <- read.csv(file = system.file(package = "rsvie", "extdata", "econ", "econ_pars_ls_15.csv")) # get long-stay costs with 1.5% discount rate
econ_raw_ss_15 <- read.csv(file = system.file(package = "rsvie", "extdata", "econ", "econ_pars_ss_15.csv"))  # get short-stay costs with 1.5% discount rate
econ_raw_ls_35 <- read.csv(file = system.file(package = "rsvie", "extdata", "econ", "econ_pars_ls_35.csv"))  # get long-stay costs with 3.5% discount rate
econ_raw_ss_35 <- read.csv(file = system.file(package = "rsvie", "extdata", "econ", "econ_pars_ss_35.csv"))  # get short-stay costs with 3.5% discount rate

risks_vhr_raw <- read.csv(file = system.file(package = "rsvie", "extdata", "econ",  "outcome_risks_vhr.csv")) 
outcomes_incidence <- read.csv(file = system.file(package = "rsvie", "extdata", "econ", "outcomes_incidence.csv"))
outcomes_incidence_high_mort <- read.csv(file = system.file(package = "rsvie", "extdata", "econ", "outcomes_incidence_high_mort.csv")) # high mortality estimates 

model_cases_sample_mean_get <- load(file = system.file(package = "rsvie", "extdata", "model_cases_sample_mean.RData"))
model_cases_sample_mean <- get(model_cases_sample_mean_get)

# This function then converts the incidence of the outcome to the risk per infection
risks_raw <- covert_raw_to_risk(RSVempty, outcomes_incidence, model_cases_sample_mean)
risks_raw_high_mort <- covert_raw_to_risk(RSVempty, outcomes_incidence_high_mort, model_cases_sample_mean)

# initialiate all the different programmes 
RSVempty_ls_15 <- add_economics(RSVempty, econ_name = "E_W2023", econ_raw_ls_15, risks_raw, risks_vhr_raw)
RSVempty_ss_15 <- add_economics(RSVempty, econ_name = "E_W2023", econ_raw_ss_15, risks_raw, risks_vhr_raw)
RSVempty_ls_35 <- add_economics(RSVempty, econ_name = "E_W2023", econ_raw_ls_35, risks_raw, risks_vhr_raw)
RSVempty_ss_35 <- add_economics(RSVempty, econ_name = "E_W2023", econ_raw_ss_35, risks_raw, risks_vhr_raw)
RSVempty_ls_high_mort_15 <- add_economics(RSVempty, econ_name = "E_W2023", econ_raw_ls_15, risks_raw_high_mort, risks_vhr_raw)
RSVempty_ls_high_mort_35 <- add_economics(RSVempty, econ_name = "E_W2023", econ_raw_ls_35, risks_raw_high_mort, risks_vhr_raw)
RSVempty_ss_15@econ_par$discount_rate <- 0.015
RSVempty_ls_15@econ_par$discount_rate <- 0.015
RSVempty_ls_high_mort_15@econ_par$discount_rate <- 0.015

# Get the immune profile
immune_profile <- readRDS(file = system.file(package = "rsvie", "extdata", "efficacies", "immune_profiles_unbound.RDS"))


# Older adult vaccination programmes
# short stay
run_scenarios_oa(RSVempty_ss_35, immune_profile, "oa_unbound_ss_dr35", cov = c(0.7)); cat(1)
run_scenarios_oa(RSVempty_ss_15, immune_profile, "oa_unbound_ss_dr15", cov = c(0.7)); cat(2)

# long-stay stay
run_scenarios_oa(RSVempty_ls_35, immune_profile, "oa_unbound_ls_dr35", cov = c(0.7)); cat(1)
run_scenarios_oa(RSVempty_ls_15, immune_profile, "oa_unbound_ls_dr15", cov = c(0.7)); cat(2)

# high moartality with long stay
run_scenarios_oa(RSVempty_ls_high_mort_35, immune_profile, "oa_unbound_ls_dr35_high", cov = c(0.7))
run_scenarios_oa(RSVempty_ls_high_mort_15, immune_profile, "oa_unbound_ls_dr15_high", cov = c(0.7))


```